% Bryan Bugyi --- Resume (Batman / Dossier Modern variant, v2).
%
% Layout heritage: original article-class resume scaffolding by
%   (c) 2002 Matthew Boedicker <mboedick@mboedick.org>
%   (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com>
%   (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com>
% This work is licensed under CC BY-NC-SA 2.5
% (http://creativecommons.org/licenses/by-nc-sa/2.5/).
%
% Substantially rewritten 2026 for typographic refinement: EB Garamond body,
% IBM Plex Sans display, IBM Plex Mono accents, gold leader-rule section
% headings, restrained Gotham palette, single fontawesome5 ornament.

\documentclass[letterpaper,11pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Geometry
\usepackage[letterpaper,margin=0.75in,top=0.6in,bottom=0.6in]{geometry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Gotham Palette
\usepackage[svgnames]{xcolor}
\definecolor{batblack}{HTML}{0B0B0F}
\definecolor{batink}{HTML}{1F1F24}
\definecolor{batgold}{HTML}{D4A017}
\definecolor{batgoldlight}{HTML}{F5C518}
\definecolor{batstone}{HTML}{6B6B73}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Typography
\usepackage{ebgaramond}    % Body serif
\usepackage{plex-sans}     % Display sans
\usepackage{plex-mono}     % Mono accents
\usepackage{microtype}

% gutils brings amsmath, amssymb, amsthm, bm, enumitem, float, graphicx,
% listings, ulem, xparse plus the \declarecommand macro.
\input{/home/bryan/Sync/lib/latex/gutils.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Layout / structure packages
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{fontawesome5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Page style
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{{\sffamily\scshape\color{batstone}\fontsize{8.5pt}{10pt}\selectfont\thepage}}

\raggedbottom
\raggedright
\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}
\frenchspacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Section heading
\newcommand{\resheading}[1]{%
  \par\addvspace{14pt}%
  \noindent
  {\sffamily\bfseries\color{batgold}\fontsize{11pt}{13pt}\selectfont%
   \textls*[150]{\MakeUppercase{#1}}}%
  \hspace{0.6em}%
  {\color{batgold}\leaders\hrule height 0.6pt\hfill\kern0pt}%
  \par\nobreak\addvspace{4pt}%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bullets
\setlist[itemize,1]{
  label={\textcolor{batgold}{\small\faCaretRight}},
  leftmargin=1.4em, topsep=2pt, itemsep=2pt, parsep=0pt
}
\setlist[itemize,2]{
  label={\textcolor{batstone}{\textendash}},
  leftmargin=1.2em, topsep=1pt, itemsep=1pt, parsep=0pt
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Custom commands
\newcommand{\midsep}{\,\textcolor{batstone}{$\cdot$}\,}

% Job subheading: company / location / role / dates.
\newcommand{\ressubheading}[4]{%
  \par\addvspace{4pt}%
  \noindent
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    {\sffamily\bfseries\color{batblack}\fontsize{11pt}{13pt}\selectfont #1} &
    {\sffamily\color{batstone}\fontsize{10pt}{12pt}\selectfont #2} \\[1pt]
    {\itshape\color{batink}\fontsize{11pt}{13pt}\selectfont #3} &
    {\sffamily\scshape\color{batstone}\fontsize{9.5pt}{11.5pt}\selectfont #4}
  \end{tabular*}\par\vspace{-2pt}
}

% Project subheading: name / tech-stack-in-mono / tagline / dates.
\newcommand{\projsubheading}[4]{%
  \par\addvspace{4pt}%
  \noindent
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    {\sffamily\bfseries\color{batblack}\fontsize{11pt}{13pt}\selectfont #1} &
    {\ttfamily\color{batstone}\fontsize{9pt}{11pt}\selectfont #2} \\[1pt]
    {\itshape\color{batink}\fontsize{11pt}{13pt}\selectfont #3} &
    {\sffamily\scshape\color{batstone}\fontsize{9.5pt}{11.5pt}\selectfont #4}
  \end{tabular*}\par\vspace{-2pt}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Hyperlinks (load last)
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=batgold,
  linkcolor=batgold,
  citecolor=batgold,
  pdftitle={Bryan Bugyi --- Resume},
  pdfauthor={Bryan Bugyi}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  MASTHEAD
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
{\sffamily\bfseries\fontsize{28pt}{30pt}\selectfont\color{batblack}Bryan Bugyi}%
\hfill
\begin{minipage}[b]{2.4in}
  \raggedleft
  {\sffamily\color{batink}\fontsize{10pt}{13pt}\selectfont\scshape%
   \textls*[120]{Software Engineer}\\[1pt]
   \textls*[120]{Agentic-AI Tooling}}
\end{minipage}

\vspace{6pt}
\noindent\textcolor{batgold}{\rule{\textwidth}{0.8pt}}
\vspace{2pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  CONTACT STRIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
{\sffamily\color{batink}\fontsize{10pt}{12pt}\selectfont%
\textcolor{batgold}{\faEnvelope}\,\,\href{mailto:bryanbugyi34@gmail.com}{bryanbugyi34@gmail.com}%
\midsep
\textcolor{batgold}{\faPhone}\,\,(609)~500-7081%
\midsep
\textcolor{batgold}{\faGithub}\,\,\href{https://github.com/bbugyi200}{bbugyi200}%
\midsep
\textcolor{batgold}{\faLinkedin}\,\,\href{https://linkedin.com/in/bryan-bugyi}{bryan-bugyi}%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  EPIGRAPH + ORNAMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{14pt}
\begin{center}
{\color{batink}\rule[0.55ex]{2.0in}{0.3pt}}\,\,\raisebox{-0.15ex}{\textcolor{batgoldlight}{\large\faMask}}\,\,{\color{batink}\rule[0.55ex]{2.0in}{0.3pt}}\\[5pt]
{\itshape\color{batink}\fontsize{10.5pt}{13pt}\selectfont``Why do we fall, sir?\ So that we can learn to pick ourselves up.''}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  DOSSIER (summary)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Dossier}
Software engineer with seven years shipping production Python, Linux, and distributed-systems work across Google, Bloomberg, and Edgestream. Current focus: \textbf{agentic-AI developer tooling}~--- architecting \textbf{\texttt{sase}}, a multi-agent software-engineering toolkit that orchestrates Claude Code, Gemini CLI, and Codex into a managed pipeline, translating recent agentic-coding research into a tool used daily for real engineering work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  TRAINING (education)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Training}
\ressubheading{Rutgers University}{New Brunswick, NJ}{B.S.\ Computer Science (minor in Mathematics)}{September 2015 -- May 2019}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  CASEWORK (industry experience)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Casework}

\ressubheading{Google}{Manhattan, NY}{Software Engineer}{June 2022 -- present}
\begin{itemize}
  \item Full-stack engineer on Google Ad Manager; Java on the backend, Dart / AngularDart / Sass on the frontend.
\end{itemize}

\ressubheading{Bloomberg L.P.}{Manhattan, NY}{Site Reliability Engineer / Senior Software Engineer}{January 2021 -- May 2022}
\begin{itemize}
  \item Founding engineer on the Compliance SRE (CSRE) team; technical lead across the team's Python portfolio.
  \item Maintained Bloomberg's firm-wide Python cookiecutter, shaping new-project scaffolding across the company.
  \item Authored the ``ChangeLog Driven Release'' (CLDR) methodology; adopted in alpha across the Compliance department.
\end{itemize}

\ressubheading{Edgestream Partners, L.P.}{Princeton, NJ}{Software Engineer}{May 2019 -- January 2021}
\begin{itemize}
  \item Led integration of \texttt{pylint} into a 1M+ line Python trading codebase; built the supporting tooling to make it stick.
  \item Lead developer of Edgestream's Django-based investor-facing web portal.
  \item Delivered large-scale improvements to the production team's in-house testing framework and test runner.
\end{itemize}

\ressubheading{Comcast}{Mount Laurel, NJ}{Tier III Technical Support}{2011 -- 2016}
\begin{itemize}
  \item Diagnosed large-scale network outages; automated recurring team workflows (ticketing, spreadsheet parsing, info retrieval) with Python.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  UTILITY BELT (skills)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Utility Belt}
\noindent
\begin{tabularx}{\textwidth}{@{}>{\sffamily\scshape\color{batgold}\fontsize{9.5pt}{13pt}\selectfont}p{1.55in}@{\hspace{0.4em}}>{\fontsize{10.5pt}{13pt}\selectfont}X@{}}
AI / Agentic Systems & Claude Code\,$\cdot$\,Gemini CLI\,$\cdot$\,Codex\,$\cdot$\,prompt engineering\,$\cdot$\,LLM orchestration\,$\cdot$\,multi-agent workflow design \\[2pt]
Primary              & Python\,$\cdot$\,Linux\,$\cdot$\,TCP/IP networking\,$\cdot$\,Bash \\[2pt]
Working              & C/C++\,$\cdot$\,Rust\,$\cdot$\,Perl\,$\cdot$\,Java\,$\cdot$\,JavaScript\,$\cdot$\,Haskell\,$\cdot$\,Vimscript \\[2pt]
Tools                & Docker\,$\cdot$\,Git\,$\cdot$\,PostgreSQL\,$\cdot$\,Redis\,$\cdot$\,\LaTeX{}\,$\cdot$\,Vim\,$\cdot$\,Prometheus / Grafana \\[2pt]
Frameworks           & Django\,$\cdot$\,FastAPI\,$\cdot$\,Flask\,$\cdot$\,Pluggy\,$\cdot$\,ZeroMQ\,$\cdot$\,Textual \\
\end{tabularx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  FIELD WORK (open-source projects)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Field Work}

\projsubheading{sase --- Structured Agentic Software Engineering}{Python}{Multi-agent toolkit orchestrating Claude, Gemini, and Codex.}{2025--present}
\begin{itemize}
  \item Architected the full system: \textbf{ACE} (multi-agent supervision TUI built on Textual), the \textbf{AXE} daemon, and a YAML-driven workflow engine that turns natural-language prompts into structured, multi-step agentic work.
  \item Built a \texttt{pluggy}-based plugin system for VCS / workspace integrations (Git, GitHub, Chezmoi, Telegram, Gemini, Neovim), Prometheus telemetry surfacing 33 pipeline metrics, and a bead-based issue tracker for agent-owned task queues.
  \item Grounded in current agentic-coding research (Hassan et~al.\ 2025; Vaziri et~al.\ 2024)~--- translating paper ideas into tools I ship software with daily.
\end{itemize}

\projsubheading{python-boltons/*}{Python}{Python libraries we think should be ``builtins''.}{2021--present}
\begin{itemize}
  \item Founder and lead developer of this series of projects. Notable boltons:
  \vspace{-0.40cm}
  \begin{multicols}{3}
    \begin{itemize}
      \item cc-python (cookiecutter)
      \item clack (config CLI lib)
      \item eris (error-handling lib)
      \item hush (plugin secrets lib)
      \item logrus (logging lib)
    \end{itemize}
  \end{multicols}
  \vspace{-0.40cm}
\end{itemize}

\projsubheading{psf/black}{Python}{The uncompromising Python code formatter.}{2019--2021}
\begin{itemize}
  \item Rewrote black's string-handling logic ($\sim$3{,}500 LoC) in \href{https://github.com/psf/black/pull/1132}{PR \#1132}; closed five unrelated user-filed issues in one shot.
\end{itemize}

\projsubheading{bbugyi200/funky}{Python, Shell}{Makes shell functions easier to define, more flexible, and more interactive.}{2017--2021}
\begin{itemize}
  \item 500+ GitHub stars; accepted multiple external contributions (issues, bug reports, code).
\end{itemize}

\projsubheading{bbugyi200/*}{Python, Rust, Shell}{Miscellaneous open-source projects on GitHub.}{2017--present}
\begin{itemize}
  \item \texttt{greatday} (GTD todo manager)\,$\cdot$\,\texttt{cldr} (ChangeLog Driven Releases)\,$\cdot$\,\texttt{shv} (Rust shell-history viewer)\,$\cdot$\,\texttt{cookie} (templated file generator, 250+ stars).
\end{itemize}

\end{document}
